\begin{thebibliography}{9}

\bibitem{dmvn3d}
Cuong Nguyen, Yuzhen Niu, and Feng Liu. \textbf{Direct Manipulation Video Navigation in 3D}. ACH CHI 2013.

\bibitem{dmvn}
Dragicevic, P., Ramos, G., Bibliowitcz, J., Nowrouzezahrai, D., Balakrishnan, R., and Singh, K. \textbf{Video browsing by direct manipulation}. ACM CHI 2008, 237-246.

\bibitem{matlinsys}
Author Unknown. \textit{Solving Systems of Linear Equations Using Matrices}. \url{https://www.mathsisfun.com/algebra/systems-linear-equations-matrices.html}.

\bibitem{fatfinger}
Cuong Nguyen, Yuzhen Niu, and Feng Liu. \textbf{Direct Manipulation Video Navigation on Touch Screens}. ACM MobileHCI 2014.

\bibitem{staticweb}
Wikipedia. \textit{Static web page}. \url{https://en.wikipedia.org/wiki/Static_web_page}.

\bibitem{dynamicweb}
Wikipedia. \textit{Dynamic web page}. \url{https://en.wikipedia.org/wiki/Dynamic_web_page}.

\bibitem{h264}
Wikipedia. \textit{H.264/MPEG-4 AVC}. \url{https://en.wikipedia.org/wiki/H.264/MPEG-4_AVC}.

\bibitem{responsetime}
Nielsen Norman Group. \textit{Response Times: The 3 Important Limits}. \url{https://www.nngroup.com/articles/response-times-3-important-limits/}.

\bibitem{opticalflow}
Wikipedia. \textit{Optical flow}. \url{https://en.wikipedia.org/wiki/Optical_flow}.

\bibitem{http}
Wikipedia. \textit{Hypertext Transfer Protocol}. \url{https://en.wikipedia.org/wiki/Hypertext_Transfer_Protocol}.

\bibitem{html}
Wikipedia. \textit{HTML}. \url{https://en.wikipedia.org/wiki/HTML}.

\bibitem{css}
Wikipedia. \textit{Cascading Style Sheets}. \url{https://en.wikipedia.org/wiki/Cascading_Style_Sheets}.

\bibitem{dom}
Wikipedia. \textit{Document Object Model}. \url{https://en.wikipedia.org/wiki/Document_Object_Model}.

\bibitem{json}
Wikipedia. \textit{JSON}. \url{https://en.wikipedia.org/wiki/JSON}.

\bibitem{javascript}
Wikipedia. \textit{JavaScript}. \url{https://en.wikipedia.org/wiki/JavaScript}.

\bibitem{webgl}
Wikipedia. \textit{WebGL}. \url{https://en.wikipedia.org/wiki/WebGL}.

\bibitem{opengl}
Wikipedia. \textit{OpenGL}. \url{https://en.wikipedia.org/wiki/OpenGL}.

\bibitem{opengles2}
Khronos. \textit{OpenGL ES Common Profile Specification, Version 2.0.25}. \url{https://www.khronos.org/registry/OpenGL/specs/es/2.0/es_full_spec_2.0.pdf}.

\bibitem{linearinterp}
Wikipedia. \textit{Bilinear interpolation}. \url{https://en.wikipedia.org/wiki/Bilinear_interpolation}.

\bibitem{coordinatesystem}
Wikipedia. \textit{Coordinate system}. \url{https://en.wikipedia.org/wiki/Coordinate_system}.

\bibitem{domcoords}
Mozilla Developer Network. \textit{Element.getBoundingRect()}. \url{https://developer.mozilla.org/en-US/docs/Web/API/Element/getBoundingClientRect}.

\bibitem{changeofbasis}
Wikipedia. \textit{Change of basis}. \url{https://en.wikipedia.org/wiki/Change_of_basis}.

\bibitem{xformmat}
Wikipedia. \textit{Transformation matrix}. \url{https://en.wikipedia.org/wiki/Transformation_matrix}.

\bibitem{parametriceq}
Wikipedia. \textit{Parametric equation}. \url{https://en.wikipedia.org/wiki/Parametric_equation}.

\bibitem{systems}
Wikipedia. \textit{System of linear equations}. \url{https://en.wikipedia.org/wiki/System_of_linear_equations}.

\bibitem{fusion}
Wikipedia. \textit{Sensor fusion}. \url{https://en.wikipedia.org/wiki/Sensor_fusion}.

\bibitem{motion}
Mozilla Developer Network. \textit{Detecting device orientation}. \url{https://developer.mozilla.org/en-US/docs/Web/API/Detecting_device_orientation}.

\bibitem{bson}
Wikipedia. \textit{BSON}. \url{https://en.wikipedia.org/wiki/BSON}.

\bibitem{reduction}
Wikipedia. \textit{Graph reduction}. \url{https://en.wikipedia.org/wiki/Graph_reduction}.

\bibitem{h264}
Wikipedia. \textit{H.264/MPEG-4 AVC}. \url{https://en.wikipedia.org/wiki/H.264/MPEG-4_AVC}.

\bibitem{ycbcr}
Wikipedia. \textit{YCbCr}. \url{https://en.wikipedia.org/wiki/YCbCr}.

\end{thebibliography}

